Efficient implementation of kernel filtering

### 2007-08-07 article/Article.tex
add threading perf for the fastRankMean filters and update consolidatedMorphology perf2D results to include separable basic algorithm, and use the  right name for the iterative alogrithm
darcs-hash:20070807151858-2fc9d-d60c71adc0bf995f6a546a1404c8b2b2a6e3295d.gz

\begin{figure}[htbp]
\begin{center}
\subfigure[Mean]{\includegraphics[scale=0.62]{fastRankMean-perfMean}}
\subfigure[Median]{\includegraphics[scale=0.62]{fastRankMean-perfMedian}}
\caption{Execution times for several algorithms of mean filters (a) and
median filters (b).\label{fig:perfRank}
Results are reported in Tables \ref{tab:perfRankMean} and  \ref{tab:perfRankMedian}.}
\end{center}
\end{figure}

@@

\begin{table}[phtb]
\centering
\begin{tabular}{ccccccc}
\hline
Radius	&	Basic	&	Separable	&	Histogram	&	Separable histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	0.00477	&	0.00491	&	0.013	&	0.012	&	0.0144	&	0.00725	\\
2	&	0.0114	&	0.0101	&	0.0161	&	0.0119	&	0.0135	&	0.00743	\\
3	&	0.024	&	0.0146	&	0.0193	&	0.0116	&	0.0129	&	0.00794	\\
4	&	0.0444	&	0.0192	&	0.0231	&	0.0114	&	0.0126	&	0.00755	\\
5	&	0.0714	&	0.0247	&	0.0261	&	0.0114	&	0.0121	&	0.0074	\\
6	&	0.107	&	0.0299	&	0.0313	&	0.0116	&	0.0127	&	0.00771	\\
7	&	0.153	&	0.034	&	0.0358	&	0.0113	&	0.0121	&	0.00859	\\
8	&	0.211	&	0.0407	&	0.038	&	0.0112	&	0.0121	&	0.00773	\\
9	&	0.281	&	0.0442	&	0.0434	&	0.0114	&	0.012	&	0.00779	\\
10	&	0.365	&	0.0486	&	0.0446	&	0.0111	&	0.0118	&	0.00763	\\
15	&	1.03	&	0.074	&	0.0604	&	0.0115	&	0.0116	&	0.00794	\\
20	&	2.23	&	0.104	&	0.079	&	0.0113	&	0.0113	&	0.00762	\\
25	&	4.11	&	0.129	&	0.0968	&	0.0114	&	0.0116	&	0.0079	\\
30	&	6.82	&	0.154	&	0.111	&	0.0114	&	0.0115	&	0.00781	\\
40	&	15.4	&	0.214	&	0.153	&	0.0116	&	0.0116	&	0.00785	\\
50	&	29.3	&	0.285	&	0.19	&	0.0119	&	0.0117	&	0.00804	\\
100	&	226	&	0.767	&	0.355	&	0.0129	&	0.0117	&	0.00809	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for dilation by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perfDilation}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Radius	&	Basic	&	Histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	0.0107	&	0.0124	&	0.0219	&	0.014	\\
2	&	0.0235	&	0.0167	&	0.0201	&	0.0144	\\
3	&	0.0488	&	0.0211	&	0.019	&	0.0154	\\
4	&	0.0895	&	0.0247	&	0.0184	&	0.0148	\\
5	&	0.143	&	0.0273	&	0.0176	&	0.0143	\\
6	&	0.216	&	0.037	&	0.0184	&	0.0149	\\
7	&	0.308	&	0.0372	&	0.0176	&	0.0167	\\
8	&	0.423	&	0.0401	&	0.0172	&	0.015	\\
9	&	0.563	&	0.0466	&	0.0171	&	0.0151	\\
10	&	0.73	&	0.0455	&	0.0166	&	0.0148	\\
15	&	2.07	&	0.0624	&	0.0165	&	0.0153	\\
20	&	4.46	&	0.0885	&	0.0159	&	0.0148	\\
25	&	8.22	&	0.104	&	0.0163	&	0.0153	\\
30	&	13.6	&	0.118	&	0.0161	&	0.0151	\\
40	&	30.9	&	0.153	&	0.0163	&	0.0153	\\
50	&	58.6	&	0.196	&	0.0168	&	0.0156	\\
100	&	452	&	0.339	&	0.0163	&	0.0157	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological gradient transformation by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perfGradient}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Radius	&	Basic	&	Histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	0.0105	&	0.0208	&	0.0167	&	0.0146	\\
2	&	0.0217	&	0.0283	&	0.0157	&	0.0148	\\
3	&	0.0424	&	0.0352	&	0.0145	&	0.0154	\\
4	&	0.0752	&	0.0444	&	0.0142	&	0.0159	\\
5	&	0.117	&	0.049	&	0.0143	&	0.0159	\\
6	&	0.172	&	0.0573	&	0.014	&	0.0162	\\
7	&	0.24	&	0.0676	&	0.0139	&	0.0165	\\
8	&	0.324	&	0.072	&	0.0141	&	0.0169	\\
9	&	0.425	&	0.0804	&	0.0141	&	0.0175	\\
10	&	0.546	&	0.093	&	0.0143	&	0.0176	\\
15	&	1.5	&	0.14	&	0.0154	&	0.019	\\
20	&	3.19	&	0.178	&	0.0155	&	0.0204	\\
25	&	5.9	&	0.235	&	0.0164	&	0.0219	\\
30	&	9.9	&	0.274	&	0.0175	&	0.0236	\\
40	&	23	&	0.383	&	0.0193	&	0.0272	\\
50	&	45.3	&	0.522	&	0.0213	&	0.0298	\\
100	&	421	&	1.6	&	0.0346&		0.0493	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological opening by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perfOpening}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Threads	&	Basic	&	Histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	3.37	&	2.34	&	1.23	&	1.02	\\
2	&	1.69	&	1.64	&	0.73	&	0.615	\\
3	&	1.14	&	1.15	&	0.46	&	0.367	\\
4	&	0.871	&	0.866	&	0.39	&	0.312	\\
5	&	1.06	&	1.03	&	0.505	&	0.437	\\
6	&	1.01	&	0.949	&	0.489	&	0.422	\\
7	&	0.963	&	0.866	&	0.493	&	0.422	\\
8	&	0.918	&	0.849	&	0.506	&	0.453	\\
9	&	0.947	&	0.897	&	0.548	&	0.491	\\
10	&	0.92	&	0.874	&	0.568	&	0.506	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological opening by boxes using several algorithm implementations applied to the $3200 \times 2400$ image.\label{tab:perfThreads}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{cccc}
\hline
Radius	&	Histogram	&	van Herk / Gil Werma	&	Anchorn	\\
\hline
1	&	0.354	&	0.379	&	0.532	\\
2	&	0.486	&	0.329	&	0.455	\\
3	&	0.62	&	0.338	&	0.411	\\
4	&	0.74	&	0.763	&	0.995	\\
5	&	0.862	&	0.757	&	0.95	\\
6	&	1.03	&	0.759	&	0.968	\\
7	&	1.17	&	0.77	&	0.936	\\
8	&	1.31	&	0.768	&	0.894	\\
9	&	1.52	&	1.11	&	1.28	\\
10	&	1.67	&	1.08	&	1.31	\\
15	&	2.42	&	1.09	&	1.25	\\
20	&	3.13	&	1.16	&	1.29	\\
25	&	3.84	&	1.14	&	1.26	\\
30	&	4.64	&	1.17	&	1.3	\\
40	&	5.95	&	1.19	&	1.23	\\
50	&	7.6	&	1.22	&	1.41	\\
100	&	19	&	1.36	&	1.34	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological opening by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perf2Dpoly}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Radius	&	Direct	&	Moving window	&	Separable direct	&	Separable moving window	\\
\hline
1	&	0.00355	&	0.00498	&	0.00487	&	0.00668	\\
2	&	0.00642	&	0.00706	&	0.0054	&	0.00679	\\
3	&	0.0127	&	0.00761	&	0.00861	&	0.00756	\\
5	&	0.0259	&	0.00936	&	0.00803	&	0.00749	\\
10	&	0.121	&	0.0162	&	0.0129	&	0.00765	\\
15	&	0.35	&	0.0224	&	0.0206	&	0.00755	\\
20	&	0.771	&	0.0252	&	0.0278	&	0.0076	\\
40	&	5.59	&	0.059	&	0.0699	&	0.00871	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for mean filters using direct and sliding window implementations applied to the $256 \times 256$ cthead image.\label{tab:perfRankMean}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Radius	&	Direct	&	Huang	&	Separable direct	&	Separable huang	\\
\hline
1	&	0.00642	&	0.00758	&	0.0071	&	0.0093	\\
5	&	0.0448	&	0.0186	&	0.0153	&	0.00913	\\
10	&	0.177	&	0.0265	&	0.0291	&	0.00895	\\
15	&	0.445	&	0.0342	&	0.0362	&	0.00876	\\
20	&	0.93	&	0.043	&	0.0444	&	0.00925	\\
40	&	6.21	&	0.061	&	0.0899	&	0.00936	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for median filters using direct and sliding window implementations applied to the $256 \times 256$ cthead image. The separable median is an approximation and therefore doesn't produce the same result as the direct or sliding algorithms.\label{tab:perfRankMedian}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Size  &  Direct Mean &  Box Mean & Direct sigma & Box sigma\\
1	&	0.557	&	0.916	&	0.858	&	1.45	 \\
2	&	1.15	&	0.924	&	1.64	&	1.56	 \\
3	&	2.08	&	0.932	&	2.74	&	1.56	 \\
4	&	3.47	&	0.92	&	4.34	&	1.55	 \\
5	&	5.13	&	0.935	&	6.34	&	1.55	 \\
6	&	7.06	&	1.08	&	8.53	&	1.62	 \\
7	&	9.42	&	1.08	&	11.3	&	1.63	 \\
8	&	12.2	&	0.922	&	14.5	&	1.63	 \\
9	&	15.3	&	0.924	&	18	&	1.63	 \\
10	&	18.9	&	0.925	&	22.1	&	1.63	 \\
15	&	43.3	&	0.929	&	50.2	&	1.64	 \\
20	&	80.1	&	0.936	&	91.8	&	1.64	 \\
25	&	131	&	0.939	&	149	&	1.64	 \\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for mean and standard deviation using direct and box convolution implementations applied to the $3200 \times 2400$ image.\label{tab:perfBoxConv}}
\end{table}

\begin{table}[phtb]
\centering
\begin{tabular}{ccccc}
\hline
Size  &  Direct Mean &  Box Mean & Direct sigma & Box sigma\\
\hline
1	&	2.1	&	0.942	&	2.75	&	1.57	\\
2	&	1.06	&	0.466	&	1.38	&	0.805	\\
3	&	0.716	&	0.391	&	0.932	&	0.551	\\
4	&	0.538	&	0.335	&	0.846	&	0.453	\\
5	&	0.659	&	0.327	&	0.902	&	0.525	\\
6	&	0.616	&	0.298	&	0.728	&	0.47	\\
7	&	0.579	&	0.285	&	0.758	&	0.466	\\
8	&	0.558	&	0.27	&	0.729	&	0.473	\\
9	&	0.614	&	0.289	&	0.771	&	0.467	\\
10	&	0.578	&	0.281	&	0.732	&	0.476	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for mean and standard deviation using direct and box convolution implementations applied to the $3200 \times 2400$ image.\label{tab:perfBoxConv-threads}}
\end{table}

>>>>

\begin{figure}[htbp]
\begin{center}
\subfigure[Mean]{\includegraphics[scale=0.62]{fastRankMean-perfMean}}
\subfigure[Median]{\includegraphics[scale=0.62]{fastRankMean-perfMedian}}
\subfigure[Threads]{\includegraphics[scale=0.62]{fastRankMean-perf_threads-large}}
\caption{Execution times for an increasing kernel size with several algorithms of mean filters (a) and
median filters (b). Excution times with an an increasing number of threads (c).\label{fig:perfRank}
Results are reported in Tables \ref{tab:perfRankMean}, \ref{tab:perfRankMedian}
and \ref{tab:perfRankThreads}.}
\end{center}
\end{figure}

@@

\begin{table}[phtb]
\centering
\small
\begin{tabular}{cccccccc}
\hline
Radius	&	Basic	&	Iterative	&	Separable	&	Histogram	&	Separable histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	0.00437	&	0.00436	&	0.00734	&	0.00987	&	0.0121	&	0.0111	&	0.00715	\\
2	&	0.0118	&	0.00872	&	0.00901	&	0.0131	&	0.0121	&	0.0101	&	0.00733	\\
3	&	0.0241	&	0.013	&	0.0108	&	0.0161	&	0.0118	&	0.00979	&	0.00756	\\
4	&	0.0446	&	0.0175	&	0.0127	&	0.0213	&	0.0117	&	0.00922	&	0.00736	\\
5	&	0.0718	&	0.0219	&	0.0149	&	0.0237	&	0.0116	&	0.00923	&	0.00768	\\
6	&	0.107	&	0.0262	&	0.017	&	0.0262	&	0.0114	&	0.00906	&	0.00768	\\
7	&	0.154	&	0.0311	&	0.0192	&	0.0315	&	0.0113	&	0.00899	&	0.00779	\\
8	&	0.211	&	0.0349	&	0.0223	&	0.0334	&	0.0115	&	0.00865	&	0.00759	\\
9	&	0.281	&	0.0395	&	0.0246	&	0.0385	&	0.0113	&	0.00892	&	0.00784	\\
10	&	0.365	&	0.0441	&	0.0273	&	0.0399	&	0.0113	&	0.0086	&	0.00767	\\
15	&	1.03	&	0.0668	&	0.0451	&	0.0585	&	0.0115	&	0.00851	&	0.00798	\\
20	&	2.23	&	0.0895	&	0.0657	&	0.0761	&	0.0118	&	0.00819	&	0.0077	\\
25	&	4.11	&	0.114	&	0.0911	&	0.0958	&	0.0114	&	0.00826	&	0.00778	\\
30	&	6.84	&	0.139	&	0.121	&	0.108	&	0.0115	&	0.00847	&	0.00801	\\
40	&	15.5	&	0.194	&	0.195	&	0.145	&	0.0116	&	0.00872	&	0.00811	\\
50	&	29.4	&	0.257	&	0.283	&	0.185	&	0.0118	&	0.00858	&	0.00798	\\
100	&	227	&	0.719	&	0.974	&	0.348	&	0.0127	&	0.00858	&	0.0082	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for dilation by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perfDilation}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Radius	&	Basic	&	Histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	0.0107	&	0.0124	&	0.0219	&	0.014	\\
2	&	0.0235	&	0.0167	&	0.0201	&	0.0144	\\
3	&	0.0488	&	0.0211	&	0.019	&	0.0154	\\
4	&	0.0895	&	0.0247	&	0.0184	&	0.0148	\\
5	&	0.143	&	0.0273	&	0.0176	&	0.0143	\\
6	&	0.216	&	0.037	&	0.0184	&	0.0149	\\
7	&	0.308	&	0.0372	&	0.0176	&	0.0167	\\
8	&	0.423	&	0.0401	&	0.0172	&	0.015	\\
9	&	0.563	&	0.0466	&	0.0171	&	0.0151	\\
10	&	0.73	&	0.0455	&	0.0166	&	0.0148	\\
15	&	2.07	&	0.0624	&	0.0165	&	0.0153	\\
20	&	4.46	&	0.0885	&	0.0159	&	0.0148	\\
25	&	8.22	&	0.104	&	0.0163	&	0.0153	\\
30	&	13.6	&	0.118	&	0.0161	&	0.0151	\\
40	&	30.9	&	0.153	&	0.0163	&	0.0153	\\
50	&	58.6	&	0.196	&	0.0168	&	0.0156	\\
100	&	452	&	0.339	&	0.0163	&	0.0157	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological gradient transformation by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perfGradient}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Radius	&	Basic	&	Histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	0.0105	&	0.0208	&	0.0167	&	0.0146	\\
2	&	0.0217	&	0.0283	&	0.0157	&	0.0148	\\
3	&	0.0424	&	0.0352	&	0.0145	&	0.0154	\\
4	&	0.0752	&	0.0444	&	0.0142	&	0.0159	\\
5	&	0.117	&	0.049	&	0.0143	&	0.0159	\\
6	&	0.172	&	0.0573	&	0.014	&	0.0162	\\
7	&	0.24	&	0.0676	&	0.0139	&	0.0165	\\
8	&	0.324	&	0.072	&	0.0141	&	0.0169	\\
9	&	0.425	&	0.0804	&	0.0141	&	0.0175	\\
10	&	0.546	&	0.093	&	0.0143	&	0.0176	\\
15	&	1.5	&	0.14	&	0.0154	&	0.019	\\
20	&	3.19	&	0.178	&	0.0155	&	0.0204	\\
25	&	5.9	&	0.235	&	0.0164	&	0.0219	\\
30	&	9.9	&	0.274	&	0.0175	&	0.0236	\\
40	&	23	&	0.383	&	0.0193	&	0.0272	\\
50	&	45.3	&	0.522	&	0.0213	&	0.0298	\\
100	&	421	&	1.6	&	0.0346&		0.0493	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological opening by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perfOpening}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Threads	&	Basic	&	Histogram	&	Anchor	&	van Herk / Gil Werman	\\
\hline
1	&	3.37	&	2.34	&	1.23	&	1.02	\\
2	&	1.69	&	1.64	&	0.73	&	0.615	\\
3	&	1.14	&	1.15	&	0.46	&	0.367	\\
4	&	0.871	&	0.866	&	0.39	&	0.312	\\
5	&	1.06	&	1.03	&	0.505	&	0.437	\\
6	&	1.01	&	0.949	&	0.489	&	0.422	\\
7	&	0.963	&	0.866	&	0.493	&	0.422	\\
8	&	0.918	&	0.849	&	0.506	&	0.453	\\
9	&	0.947	&	0.897	&	0.548	&	0.491	\\
10	&	0.92	&	0.874	&	0.568	&	0.506	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological opening by boxes using several algorithm implementations applied to the $3200 \times 2400$ image.\label{tab:perfThreads}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{cccc}
\hline
Radius	&	Histogram	&	van Herk / Gil Werman	&	Anchorn	\\
\hline
1	&	0.354	&	0.379	&	0.532	\\
2	&	0.486	&	0.329	&	0.455	\\
3	&	0.62	&	0.338	&	0.411	\\
4	&	0.74	&	0.763	&	0.995	\\
5	&	0.862	&	0.757	&	0.95	\\
6	&	1.03	&	0.759	&	0.968	\\
7	&	1.17	&	0.77	&	0.936	\\
8	&	1.31	&	0.768	&	0.894	\\
9	&	1.52	&	1.11	&	1.28	\\
10	&	1.67	&	1.08	&	1.31	\\
15	&	2.42	&	1.09	&	1.25	\\
20	&	3.13	&	1.16	&	1.29	\\
25	&	3.84	&	1.14	&	1.26	\\
30	&	4.64	&	1.17	&	1.3	\\
40	&	5.95	&	1.19	&	1.23	\\
50	&	7.6	&	1.22	&	1.41	\\
100	&	19	&	1.36	&	1.34	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for morphological opening by boxes using several algorithm implementations applied to the $256 \times 256$ cthead image.\label{tab:perf2Dpoly}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Radius	&	Direct	&	Moving window	&	Separable direct	&	Separable moving window	\\
\hline
1	&	0.00355	&	0.00498	&	0.00487	&	0.00668	\\
2	&	0.00642	&	0.00706	&	0.0054	&	0.00679	\\
3	&	0.0127	&	0.00761	&	0.00861	&	0.00756	\\
5	&	0.0259	&	0.00936	&	0.00803	&	0.00749	\\
10	&	0.121	&	0.0162	&	0.0129	&	0.00765	\\
15	&	0.35	&	0.0224	&	0.0206	&	0.00755	\\
20	&	0.771	&	0.0252	&	0.0278	&	0.0076	\\
40	&	5.59	&	0.059	&	0.0699	&	0.00871	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for mean filters using direct and sliding window implementations applied to the $256 \times 256$ cthead image.\label{tab:perfRankMean}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Radius	&	Direct	&	Huang	&	Separable direct	&	Separable huang	\\
\hline
1	&	0.00642	&	0.00758	&	0.0071	&	0.0093	\\
5	&	0.0448	&	0.0186	&	0.0153	&	0.00913	\\
10	&	0.177	&	0.0265	&	0.0291	&	0.00895	\\
15	&	0.445	&	0.0342	&	0.0362	&	0.00876	\\
20	&	0.93	&	0.043	&	0.0444	&	0.00925	\\
40	&	6.21	&	0.061	&	0.0899	&	0.00936	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for median filters using direct and sliding window implementations applied to the $256 \times 256$ cthead image. The separable median is an approximation and therefore doesn't produce the same result as the direct or sliding algorithms.\label{tab:perfRankMedian}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccccc}
\hline
Threads	&	fastApproxMaskRank	&	fastApproxRank	&	maskedRank	&	movingWindowMean	&	rank	&	separableMean	\\
\hline
1	&	1.83	&	1.78	&	3.99	&	2.17	&	4.36	&	1.23	\\
2	&	0.921	&	0.898	&	2.02	&	1.09	&	2.21	&	0.634	\\
3	&	0.698	&	0.704	&	1.48	&	0.788	&	1.48	&	0.471	\\
4	&	0.516	&	0.505	&	1.07	&	0.559	&	1.12	&	0.403	\\
5	&	0.613	&	0.637	&	1.24	&	0.764	&	1.34	&	0.461	\\
6	&	0.582	&	0.548	&	1.12	&	0.607	&	1.17	&	0.42	\\
7	&	0.546	&	0.539	&	1.14	&	0.642	&	1.26	&	0.398	\\
8	&	0.513	&	0.506	&	1.06	&	0.598	&	1.13	&	0.402	\\
9	&	0.569	&	0.558	&	1.12	&	0.615	&	1.22	&	0.412	\\
10	&	0.558	&	0.55	&	1.07	&	0.603	&	1.16	&	0.408	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for median and mean filters using direct and sliding window implementations applied to the $3200 \times 2400$ image.\label{tab:perfRankThreads}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Size  &  Direct Mean &  Box Mean & Direct sigma & Box sigma\\
1	&	0.557	&	0.916	&	0.858	&	1.45	 \\
2	&	1.15	&	0.924	&	1.64	&	1.56	 \\
3	&	2.08	&	0.932	&	2.74	&	1.56	 \\
4	&	3.47	&	0.92	&	4.34	&	1.55	 \\
5	&	5.13	&	0.935	&	6.34	&	1.55	 \\
6	&	7.06	&	1.08	&	8.53	&	1.62	 \\
7	&	9.42	&	1.08	&	11.3	&	1.63	 \\
8	&	12.2	&	0.922	&	14.5	&	1.63	 \\
9	&	15.3	&	0.924	&	18	&	1.63	 \\
10	&	18.9	&	0.925	&	22.1	&	1.63	 \\
15	&	43.3	&	0.929	&	50.2	&	1.64	 \\
20	&	80.1	&	0.936	&	91.8	&	1.64	 \\
25	&	131	&	0.939	&	149	&	1.64	 \\
\hline
\hline
\small
\end{tabular}
\caption{Execution times in seconds for mean and standard deviation using direct and box convolution implementations applied to the $3200 \times 2400$ image.\label{tab:perfBoxConv}}
\end{table}

\begin{table}[phtb]
\centering
\small
\begin{tabular}{ccccc}
\hline
Size  &  Direct Mean &  Box Mean & Direct sigma & Box sigma\\
\hline
1	&	2.1	&	0.942	&	2.75	&	1.57	\\
2	&	1.06	&	0.466	&	1.38	&	0.805	\\
3	&	0.716	&	0.391	&	0.932	&	0.551	\\
4	&	0.538	&	0.335	&	0.846	&	0.453	\\
5	&	0.659	&	0.327	&	0.902	&	0.525	\\
6	&	0.616	&	0.298	&	0.728	&	0.47	\\
7	&	0.579	&	0.285	&	0.758	&	0.466	\\
8	&	0.558	&	0.27	&	0.729	&	0.473	\\
9	&	0.614	&	0.289	&	0.771	&	0.467	\\
10	&	0.578	&	0.281	&	0.732	&	0.476	\\
\hline
\hline
\end{tabular}
\caption{Execution times in seconds for mean and standard deviation using direct and box convolution implementations applied to the $3200 \times 2400$ image.\label{tab:perfBoxConv-threads}}
\end{table}
